\Large Postdoctoral Position Research Proposal: \\ The Role of Disk Volatile Chemistry and Dynamics in Shaping the Compositions of Nascent Planets\vspace{-2ex}

### 2016-07-20 Postdoc Applications/AnaMariaPisoResume.tex
update
upd

\section{\sc Education}
{\bf Harvard University}, Cambridge, MA \\
\begin{list1}
\vspace{-0.1in}
\item[] Ph.D., Astronomy \& Astrophysics, May 2016 (expected)
\item[] Advisor: Dr. Karin \"Oberg 
\item[] Thesis Topic: ``Dynamics and Chemistry in Protoplanetary Disks''   
\end{list1}
{\bf Harvard University}, Cambridge, MA \\
\begin{list1}
\vspace{-0.1in}
\item[] A.M., Astronomy \& Astrophysics, May 2013
\item[] Advisor: Dr. Ruth Murray-Clay
\item[] Research Exam Project: ``On the Minimum Core Mass for Giant Planet Formation''
\end{list1}
{\bf Massachusetts Institute of Technology}, Cambridge, MA\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] S.B., Physics,  June 2010 \,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\, Major GPA: 4.6/5.0
\item[] S.B., Mathematics, June 2010\,\,\,\, Major GPA: 4.8/5.0
\end{list1}

\section{\sc Research Experience \& Employment}
\begin{list2}
\item[] {\bf Research assistant} \hfill {\bf August 2010 - July 2011}
%{\bf Harvard-Smithsonian Center for Astrophysics} \hfill \textit{Cambridge, MA}
\begin{list1}
%\vspace{-0.1in}
\item[] MIT, EAPS Department \hfill \textit{Cambridge, MA}
\item[] Project: The Magnetic Field Signature of Super Earths
\item[] Advisor: Prof. Sara Seager \\
\end{list1}

@@

\begin{list2}
\item[] {\bf Piso, A.-M. A.}, \"Oberg, K. I., Birnstiel, T., \& Murray-Clay, R. A. \textit{C/O and Snowline Locations in Protoplanetary Disks: The Effect of Radial Drift and Viscous Gas Accretion}. ApJ, resubmitted after referee report \\
\end{list2}

@@

\section{\sc Publications in Preparation}

\begin{list2}
\item[] {\bf Piso, A.-M. A.}, \"Oberg, K.I., \& Pegues, J. \textit{The Role of Ice Compositions and Morphology For Snowlines and the C/N/O Ratios in Active Disks} \\
\end{list2}

@@

@@

\section{\sc Professional Activities \& Service}
%\vspace*{-.17in}
\begin{list2}
\item[] American Physical Society member
\item[] American Astronomical Society member
%\item Romanian Student Association treasurer (2007-2010)
%\item MIT International Student Orientation coordinator (2008, 2009)
\end{list2}

>>>>

\section{\sc Education}
{\bf Harvard University}, Cambridge, MA \\
\begin{list1}
\vspace{-0.1in}
\item[] Ph.D., Astronomy \& Astrophysics, May 2016
\item[] Advisor: Prof. Karin \"Oberg 
\item[] Thesis Title: ``Origins of Gas Giant Compositions: The Role of Disk Location and Dynamics''   
\end{list1}
{\bf Harvard University}, Cambridge, MA \\
\begin{list1}
\vspace{-0.1in}
\item[] A.M., Astronomy \& Astrophysics, May 2013
\item[] Advisor: Dr. Ruth Murray-Clay
\item[] Research Exam Project: ``On the Minimum Core Mass for Giant Planet Formation''
\end{list1}
{\bf Massachusetts Institute of Technology}, Cambridge, MA\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] S.B., Physics,  June 2010 \,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\, Major GPA: 4.6/5.0
\item[] S.B., Mathematics, June 2010\,\,\,\, Major GPA: 4.8/5.0
\end{list1}

\section{\sc Research Experience \& Employment}
\begin{list2}

\item[] {\bf Postdoctoral Fellow} \hfill {\bf September 2016 - }
%{\bf Harvard-Smithsonian Center for Astrophysics} \hfill \textit{Cambridge, MA}
\begin{list1}
%\vspace{-0.1in}
\item[] UCLA, Earth, Planetary and Space Sciences Department \hfill \textit{Los Angeles, CA}
%\item[] Project: The Magnetic Field Signature of Super Earths
\item[] Advisor: Prof. Hilke Schlichting \\
\end{list1}

\item[] {\bf Postdoctoral Fellow} \hfill {\bf July 2016 - August 2016}
%{\bf Harvard-Smithsonian Center for Astrophysics} \hfill \textit{Cambridge, MA}
\begin{list1}
%\vspace{-0.1in}
\item[] Harvard College Observatory  \hfill \textit{Cambridge, MA}
%\item[] Project: The Magnetic Field Signature of Super Earths
\item[] Advisor: Prof. Karin \"Oberg \\
\end{list1}

\item[] {\bf Research assistant} \hfill {\bf August 2010 - July 2011}
%{\bf Harvard-Smithsonian Center for Astrophysics} \hfill \textit{Cambridge, MA}
\begin{list1}
%\vspace{-0.1in}
\item[] MIT, EAPS Department \hfill \textit{Cambridge, MA}
\item[] Project: The Magnetic Field Signature of Super Earths
\item[] Advisor: Prof. Sara Seager \\
\end{list1}

@@

\begin{list2}
\item[] {\bf Piso, A.-M. A.}, Pegues, J., \& \"Oberg, K.I. \textit{The Role of Ice Compositions and Morphology For Snowlines and the C/N/O Ratios in Active Disks}. ApJ, submitted \\
\end{list2}

\begin{list2}
\item[] {\bf Piso, A.-M. A.}, \"Oberg, K. I., Birnstiel, T., \& Murray-Clay, R. A. \textit{C/O and Snowline Locations in Protoplanetary Disks: The Effect of Radial Drift and Viscous Gas Accretion}. ApJ, 2015, 815, 109 \\
\end{list2}

@@

%\section{\sc Publications in Preparation}

@@

\begin{list2}
\item[] {\bf Giant Planet Formation and Snowlines in Protoplanetary Disks} \\
MIT Planetary Lunch Colloquium Series, Cambridge, MA, March 2016\\
Invited talk \\
\end{list2}

\begin{list2}
\item[] {\bf The Role of Disk Volatile Chemistry and Dynamics in Shaping the Compositions of Nascent Planets} \\
AAS 227$^{th}$ Meeting, Kissimmee, FL, January 2016\\
Dissertation talk \\
\end{list2}

@@

\section{\sc Professional Activities \& Service}
%\vspace*{-.17in}
\begin{list2}
\item[] American Physical Society member
\item[] American Astronomical Society member
\item[] Reviewer for ApJ
%\item Romanian Student Association treasurer (2007-2010)
%\item MIT International Student Orientation coordinator (2008, 2009)
\end{list2}
